Non-kissing complexes and tau-tilting \\ for gentle algebras

### 2018-07-13 firstPaper/firstPaperLong/nonKissingComplex.tex
pdf differences

\enlargethispage{-.3cm}
In this section, we first fix our notations (\ref{subsec:pathAlgebra}) on quivers, path algebras, their representations, and their support $\tau$-tilting complexes (\ref{subsec:tautilting}).
We then focus on string algebras (\ref{subsec:stringGentleAlgebra} to \ref{subsec:morphismsStringModules}): following~\cite{ButlerRingel}, we present a combinatorial description of the indecomposable representations of a string algebra and of the Auslander-Reiten translation~$\tau$.
We then provide a convenient combinatorial description of the $\tau$-compatibility between string modules (\ref{sec:stringModules}).

>>>>

In this section, we first fix our notations (\ref{subsec:pathAlgebra}) on quivers, path algebras, their representations, and their support $\tau$-tilting complexes (\ref{subsec:tautilting}).
We then focus on string algebras (\ref{subsec:stringGentleAlgebra} to \ref{subsec:morphismsStringModules}): following~\cite{ButlerRingel}, we present a combinatorial description of the indecomposable representations of a string algebra and of the Auslander-Reiten translation~$\tau$.
We then provide a convenient combinatorial description of the $\tau$-compatibility between string modules (\ref{sec:stringModules}).
